# Broken Window 

## Elicitation Script

AphasiaBank Instructions -
[[https://aphasia.talkbank.org/protocol/instructions.pdf]{.ul}](https://aphasia.talkbank.org/protocol/instructions.pdf)

AphasiaBank Troubleshooting -
[[https://aphasia.talkbank.org/protocol/troubleshooting.pdf]{.ul}](https://aphasia.talkbank.org/protocol/troubleshooting.pdf)

"Now I'm going to show you these pictures.\" (Present picture series.)

"Take a little time to look at these pictures. They tell a story. Take a
look at all of them, and then I'll ask you to tell me the story with a
beginning, a middle, and an end. You can look at the pictures as you
tell the story."

If no response in 10 seconds, give second prompt: "Take a look at this
picture (point to first picture) and tell me what you think is
happening."

If needed, point to each picture sequentially, giving the prompt: "And
what happens here?"

For each panel, if no response, provide the prompt: "Can you tell me
anything about this picture?"

If no response, point to the picture and ask: "Is the boy kicking the
ball through the window?"

## Main Concept Checklist

Essential information is *italicized* and **bolded**. Each essential
segment is numbered (superscript) with alternative productions (if any
were produced) listed by number below. These alternative productions ARE
NOT intended to be an exhaustive list but represent some of the more
common productions of the normative sample and are included to aid in
scoring. Additional, but non-essential, information often spoken to
complete the main concept is in normal font. If multiple utterances can
correspond with an MC, select the best utterance presented for the
purposes of coding/scoring. 

<!-- 1)  ***^1^A/The boy ^2^was ^3^outside*.** -->

<!--     a.  *He, any name (e.g., Johnny, Mark)* -->

<!--     b.  *Is, decided to go* -->

<!--     c.  *In his yard, on the lawn, out of the house, etc.* -->

<!-- > Note: Sometimes combined with MC2 in a statement such as "The boy was -->
<!-- > playing soccer outside" or "The boy was kicking the ball in the yard". -->
<!-- > These statements would receive AC codes for MC1 and MC2. -->

```{r, echo = F, results = 'asis'}
source("stim_broken-window.R")

for(i in ls(pattern = "bw")){
  print(shiny::markdown(get(i)))
}
```

```{r, include = F}
rm("stim_broken-window.R")
```